SVG: The Paper

### 2022-05-04 Analysis/index.Rmd
scan path plot for paper

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(digits = 3)
```

@@

plt_b + plt_c + plot_layout(guides = "collect")  &
  theme(legend.position = 'right',
        legend.direction = 'horizontal')

@@

ggsave("../Figures/qjep_preds.png", 
       plt_b + plt1 + plt2 + 
         plot_layout(guides = "collect") & theme(legend.position = "bottom"),
       width = 10, height = 4)

@@

ggsave("../Figures/qjep_indiv_diff.png", 
       plt_a + plt_b + 
         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
```

@@

source("functions/plot_trial.R")
plts <- map(1:3, plot_trial, trls_easy, a, d)

plts[[1]] + plts[[2]] +
  plot_layout(nrow = 1, widths = c(1,1)) &
   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
   theme(text=element_text(size=14,  family="serif"))
```

@@

```{r fig.cap = "A random selection of *typical* trials. Along with path-minimising behaviour, we can also see some disagreement around switching item type."}
plts <- map(1:3, plot_trial, trls_mid, a, d)

plts[[1]] + plts[[2]] +
  plot_layout(nrow = 1, widths = c(1,1)) &
   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
   theme(text=element_text(size=14,  family="serif"))
```

@@

```{r fig.cap = "A random selection of *hard* trials. It is harder to make out much of a pattern here, but we can see that the human participants jump around more."}
plts <- map(1:3, plot_trial, trls_hard, a, d)

plts[[1]] + plts[[2]] +
  plot_layout(nrow = 1, widths = c(1,1)) &
   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
   theme(text=element_text(size=14,  family="serif"))
```

```{r}
rm(trls_easy, trls_mid, trls_hard, plts, qs)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(digits = 3)
set.seed(2022)
```

@@

plt_b + plt_c + plot_layout(guides = "collect")  &
  theme(legend.position = 'bottom',
        legend.direction = 'horizontal')

@@

ggsave("../Figures/qjep_preds.pdf", 
       plt_b + plt1 + plt2 + 
         plot_layout(guides = "collect") & theme(legend.position = "bottom"),
       width = 10, height = 4)

@@

ggsave("../Figures/qjep_indiv_diff.pdf", 
       plt_a + plt_b + 
         plot_layout(guides = "collect") & theme(legend.position = "right"), width = 8, height = 4)
```

@@

source("functions/plot_trial.R")
plts1 <- map(1:3, plot_trial, trls_easy, a, d)

plts1[[1]] + plts1[[2]] +
  plot_layout(nrow = 1, widths = c(1,1)) &
   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
   theme(text=element_text(size=14,  family="serif"))
```

@@

```{r fig.cap = "A random selection of *typical* trials. Along with path-minimising behaviour, we can also see some disagreement around switching item type."}
plts2 <- map(1:3, plot_trial, trls_mid, a, d)

plts2[[1]] + plts2[[2]] +
  plot_layout(nrow = 1, widths = c(1,1)) &
   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
   theme(text=element_text(size=14,  family="serif"))
```

@@

```{r fig.cap = "A random selection of *hard* trials. It is harder to make out much of a pattern here, but we can see that the human participants jump around more."}
plts3 <- map(1:3, plot_trial, trls_hard, a, d)

plts3[[1]] + plts3[[2]] +
  plot_layout(nrow = 1, widths = c(1,1)) &
   theme(plot.margin = unit(c(.2,.2,.2,.2), "cm")) &
   theme(plot.background = element_rect(color  = "#fffff8", size = 2,linetype = 'dotted', fill ="#fffff8")) &
   theme(text=element_text(size=14,  family="serif"))
```

```{r}
ggsave("../Figures/qjep_ex_paths.pdf",
      ( plts1[[1]] + plts1[[2]]) /( plts3[[1]] + plts3[[3]]), 
       width = 8, height = 8)

rm(trls_easy, trls_mid, trls_hard, plts, qs, plts1, plts2, plts3)
```
